


\thispagestyle{empty}
\pagestyle{empty} 

\begin{abstract}

\hspace{0.9cm} 
Mobile technology is widely used in all classes of society. It is the most effective way of communication. Since the dependency has increased largely, it becomes difficult to live without it. The application intends to address this problem by retrieving data from mobile handset though it is not physically available with the user. The system is designed to be controlled via SMS from anywhere that is covered by GSM service. If one’s mobile phone is not available at the moment and one needs to call a person urgently whose contact number is not available at that instant. To get that contact one has to go through very tedious process of calling home and get that contact number etc. The proposed system project helps to simplify this problem. One has to send an SMS to his/her own mobile with the contact name and automatically the contact will be returned to the same number. Also one can get location of the mobile, call log, ring the phone, get unread SMS, get the forgotten cell-phone to call back the phone from where originating message is sent and few other miscellaneous functions.

As a feature designed to prevent unauthorized access, the message needs to contain a password preset by the user. Any access of data would be stored in a local database of the phone to keep  track of who is accessing what information. Notifications would also be sent to the user to notify him/her in case of application usage. 

The application only needs to be installed and configured once. The user may completely forget about the existence of the application until there is a situation the requires the user to use it.


\end{abstract} 

