

\chapter{CONCLUSION AND FUTURE SCOPE}

\hspace{0.9cm} Thus the application is very small, simple and easy to
use by using SMS service. The best part of the system
is that it has a very low Memory Footprint i.e. it is
very light on your phone's resources. The application
overcomes the problem of 160 character length of a
message. SMS based remote control for general
purpose is beneficial for the human generation,
because mobile is most recently used technology
nowadays. The SMS based remote control for home appliances is easy to implement the system
that ON/OFF the electrical device through remotely
via SMS or it handled more and more electrical
devices which are use in home. In simple
automation system where the internet facilities and
even PC are not provided, one can use mobile
phone based control system which is simple
and cost-effective. Alternatively for such
requirements landline phone with extension card
could also be select for the system.
The application can be able to send other information
such as email ID, address and other personal details
via message using Multimedia service. One will not
need to access internet to get the personal information. \\ \\ 
\hspace{0.9 cm} The future is endless for an application of this kind as the functionality of such an application depends on the frameworks provided in the android ecosystem. We could add features like retrieval of images, videos and emails. Giving commands via a phone call is also something we researched and intend on implementing in this project in the future. \\ \\ Thank you

