

\chapter{INTRODUCTION}




\section{Background}

\hspace{0.9cm} The Android mobile operating system has, of late, become one of the most popular, free and usable systems in the world. The almost-zero cost and open source functionality has led to Android becoming one of the top contenders when it comes to the mobile OS market.
The Android mobile operating system today is used by everyone. This usage has has led to not only our dependence on our android smart phones. But also our over-dependence. Most people don’t even wear watches nowadays and use their phones to check the time. If we lose access to our device then we feel as if a part of our body is missing.
Due to the revolution in technical field of mobile phones, current mobile phones are capable of storing user data as well as sharing of information with other users. The critical user data includes call records, photos and videos as well as saved passwords of Webpages. So loosing of smart phone is not affordable to user because it cause the loss of large amount of irrecoverable data. In such scenarios, remote access to a mobile phone will be helpful to user in order to access information from mobile phone even if user is not carrying mobile phone with him. Accessing the remote data using internet connection was not a difficult task if user can carry computer every time. But in recent times, android mobile phones and smart phones have replaced the need of computers. These devices can be used not only to store user data but also capable of providing various other information like whether forecast, Google map, different chatting applications, etc. By considering a scenario where user forgets to carry mobile phone and wants to retrieve an important data from mobile phone remotely, an idea to develop a new application emerged by which user can access all required data through SMS.


\section{Objective}

\hspace{0.9cm} The primary objective of the project is to create a system which allows for easy access of our cell-phones in pre-defined cases. The user would not need to take much effort in procuring the data like messages, call logs etc. The application would also help in case of theft or misplacement by adding a location and a ring function.
Our app is designed to be a one click install in the sense that, once user sets the password he could just forget about the app till the time of need.
Real life situations-
•	Phone forgotten at home – Use message/callog command to retrieve data.
•	Phone misplaced in silent/vibrate mode – Use ring command.
•	Phone is stolen – Use lock/location command.
We propose a simple application for solving all the afore mentioned problems. Our application would request the user to set the password only during the first time opening of the application. The user may forget about our app and continue normally till the time arises when the app is needed. Our application would also be secure since it verifies the password and also stores all access requests and also access numbers.

\section{Purpose, Scope and Applicability}

\hspace{0.9cm} Our application can have a wide range of application with a fairly large amount of scalability.
Following describes its purpose,scope and applicability:

\subsection{Purpose}
\hspace{0.9cm}
 The goal of our application is to provide a quick and easy to use interface to access the phone in cases that prevent physical access to the device. This system should be available to be used with the least amount of vairable factors that can affect it. The network range of the device is the only limiting factor of the device. 
 
 \subsection{Scope}
 \begin{flushleft}
 	\textbf{Expected Outcome:} A functioning system which can access the android device via Text Messaging service.
 	
 	
 	\textbf{Required facilities :}
 	\begin{enumerate}
 		\item Android Studio
 		
 		\item Android device to test the application
 		
 		\item Ability to send and receive SMSs 
 		
 	\end{enumerate}
 	
 	\textbf{Knowledge areas needed for project:}
 	\begin{itemize}
 		\item Good proficiency in JAVA 
 		\item Experience in using Android Studio IDE 
 		\item Knowledge of android eco-system.
 		\item Knowledge of the protocols used for SMSs
 	\end{itemize}
 	
 	\textbf{The project is expected to complete in 4 months.}
 \end{flushleft}

\subsection{Applicability}
\hspace{0.9cm} The application is intended to be small and resource efficient. This allows for maximum number of installs. The application once installed need not be toyed with on a frequent basis, and the commands used by the application are easy to remember and use. It can be used in multiple situations which include forgotten phone, stolen phone, misplaced phone etc.  
 
 




