

\chapter{LITERATURE SURVEY}

\section{Literature Survey}

\hspace{0.9cm} Previously all Smartphone manufacturers used to have dedicated software to control the phone using software from their desktops. But especially with the Android smart phones, no particular software is installed. There are plenty of custom third party applications available. But now with our system we can now remotely control your phone without internet.The previous softwares need to have an Internet access. Not any application works without internet. So this type of software requires more cost. This is the biggest disadvantage of previous software. In our application we remove the disadvantage of previous software. And we develop this application which works without internet. Or we can control our android phone remotely without internet. Without using any browser. The application requires only messaging feature. And all android mobile have an inbuilt messaging feature. What you have to do is you just have to send particular command in particular format as provided in application by sending message on your remote device or remote mobile phone, then the remote mobile work according to that command. An important thing to note is the security of data. In our current world the most important product is data. As such more than the actual phone itself the people fear for the data that they have stored in the phone. This can range from memos, images, videos, emails and variety of other data. Our application is intended to not only retrieve data but also protect it in case of theft. \cite{citation-2}

\subsection{Existing System}
\hspace{0.9cm}
The new research areas for the need of the man that
controlled the electrical devices remotely, anything
from
the home such as an air conditioner, security system,
set top box, light, and so on. The case of remote
control capability and the possibility of achieving it at
a reasonably low cost have motivated the need to
research into it not only for industrial application but
also for domestic use or home use. Home wireless
security systems are becoming increasingly popular
and it is being a necessary nowadays.
The capability of controlling home
appliances in a wireless and remote fashion has
provided a great convenience to many people in life.
Through a wireless remote controller, people can do
remote operation without directly accessing the host of
a home appliance. The home appliances like fan,
lamp, television, washing machines and others. The
introduction of the Global System for Mobile
Communication (GSM) and particularly the use of
hand-held mobile phones brought the innovation of
distance communication at remote location. Based on
this, research utilizes this facility for remote control of
systems and appliances; take for instance, a man on a
journey inside his car suddenly remembers that he left
the Air Conditioner (AC), ON when it was supposed
to be OFF. The normal condition is to drive back and
switch OFF or for the home security we also monitor
the home through the system but we are not include
the option of the monitor in the system; in the system
we consider only ON and OFF operation. But with the
GSM mobile phone in the hand, one looks on how the
same could be used to effect control at any point and
time. The existing system was developed for hardware components. The existing system is the
combination of hardware and software components
both. But our proposed system works for the software
components specifically it works with the data stored
in our phone and that we require in our day-to-day
life.

\subsection{Proposed System}
\hspace{0.9cm}If you have forgotten your Cell Phone at home and you need to call a person urgently whose contact number is not available at that instant. In that case you have to call home and ask someone to search for that contact and then resend it back to you. It takes your lot of time. Instead of doing this tedious process one can send an SMS from someone’s cell to his/her own mobile in a predefined syntax.
E.g.: GET CONTACT (Contact name/initial) password
Also unread SMS can be retrieved using this application.
E.g.: password GET SMS 
Also user can get location of the mobile, Email-id, Call Log.
E.g.: password GET LOCATION 
E.g.: password GET EMAILID 
E.g.: password GET CALLLOG 
The contact name which you wish to get should write
the way it is saved in his/her contact list. If one want
multiple contacts, then send the initial of the contact
name along with the syntax and the application will
return all the contacts starting from that initial.
Also unread SMS can be retrieved using this
application. 

\subsection{Security Perspective}
\hspace{0.9cm}If one wants to get to know about this application,
he/she can steal or can make an unauthorized access
over the contacts. To secure the contacts from
unauthorized access we can set a PIN number to be
sent along with the syntax which will be known only
to you. The application will match the PIN number,
the syntax and then process and will reply back.

E.g.: 1234 GET CONTACT (contact name/initial)
Or we can use challenge response for security
purpose. In this the application will send a random
number and user will respond with a number using
challenge response. This will be predefined by the
user and saved in “SETTINGS” of the application. 

\section{Problem Definition}

\hspace{0.9cm}Most of the mobile users can’t remember their all contacts as they have a facility to save them in the phone book of their phone. This can be taken as advantage as well as a disadvantage. When user doesn’t have his/her phone with himself/herself, he/she doesn’t have access to the contacts available in that phone. It may also be possible that user doesn’t know where he/she left his/her mobile phone. In such scenario, user will waste valuable time in finding for mobile phone. If user forgets his/her mobile phone at unknown place, user may miss important phone calls or messages which can cause delay in work. Possible solutions in existing systems are: 
•	User has to travel back to his home and access all missing information. 
•	User may call to his family member or friends in case user know the place of mobile phone and access those information. 
•	Alternate solution will be to develop a mobile application by which user can able to access all information from his mobile phone remotely.

There are many cases where user places his/her phone in silent/vibrate mode and misplaces it, even in the comfort of his home. The phone could also be stolen. Our application helps during both these cases.
